---
title: "Grenfell_Door_Closers"
author: "Mick O Donnell"
date: "6/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(tidyverse)
```

# Objective

This document outlines the process required to check whether an assertion made during the Grenfell Tower Inquiry is reasonable - in order to do this, it is necessary to create a logical statement or hypothesis which we can check. There are two approaches that can be used, one via simulation and one via calculation. I will start with the former, as I have no idea as yet how to tackle the latter!

> What is the likellihood that a random sample of 7 doors from a population of 126 doors would show no defects, given that the overall defect level is 64%?

## Simulation

To simulate this situation, we will create a vector of 126 numbers, each of which is a random number between 0 and 1. We will then sample the first seven numbers repeatedly to see what proportion of these has no defects - a defect for any given door has a chance of 0.64.

I have drawn heavily from data scientist David Robinson's screencasts, which are excellent - [here](https://www.youtube.com/watch?v=pBGMt28xgvk&t=1340s)

```{r simulation}
set.seed(20210601)
# create the simulation dataframe - 1,000,000 trials
doors <- crossing(trials = 1:1000000,
                  door_check = 1:126) %>% 
  mutate(compliant = sample(c(TRUE, FALSE),
                            prob = c(0.36, 0.64),
                            replace = TRUE,
                            n()))

doors %>% 
  filter(door_check <= 7) %>% 
  group_by(trials) %>% 
  summarise(first_seven_compliant = all(compliant)) %>%
  count(first_seven_compliant)
```
In this simulation of a million trials, the first seven doors were **all** compliant 809 times, so a 0.081% chance of this happening.
